\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \begin{block}{Introduction}
        Compartmental models are often used to model disease spread in the
        population. The canonical example of such a model is the SIR model,
        which has three compartments: Susceptible, Infected, and Recovered. The
        dynamics of a population modeled by this framework are shown in
        figure~\ref{fig:SIRFlowchart}, with associated system of
        differential equations~\ref{eq:SIRdes}.
        %TODO equalize figure heights
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{Intervention Analysis}
        Intervention Analysis
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}

>>>>

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \begin{block}{Introduction}
        The most common epidemiological models are compartmental models, in
        which a system of differential equations describes how parts of the
        population move between different disease states, or
        \emph{compartments}. The canonical example of such a model is the SIR
        model, which has three compartments: Susceptible, Infected, and
        Recovered. The dynamics of a population modeled by this framework are
        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
        differential equations~\ref{eq:SIRdes}.
        %TODO equalize figure heights
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
        The SIR system, though very informative about basic disease dynamics,
        fails to capture the intricacies of more complicated diseases. This
        project examines the spread of tuberculosis (TB) in the United States
        (US) via compartmental models and stochastic, agent-based models. These
        explorations allow one to explore the impact, both epidemiological and
        economic, of various intervention strategies. These models are based on
        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
        Becerra, and K. G. Castro.
      \end{block}
      \begin{block}{The Basic Hill Model}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{Intervention Analysis}
        Intervention Analysis
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}
